Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.

### 2024-01-24 apples_and_oranges.qmd
Added meta regression F, using baseline percentage values

######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
# A) the overall sample
# B) the CBT vs Fluox and Escitalopram sample
# C) the no WL sample
# D) the no WL or CAU sample
# E) the CDRS only sample

@@

>>>>

######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
# A) the overall sample
# B) the CBT vs Fluox and Escitalopram sample
# C) the no WL sample
# D) the no WL or CAU sample
# E) the CDRS only sample
# F) percentage variables

@@

# F. Estimate Means and CIs for the overall sample using baseline percentage variable ----------------------------------

# count studies - same as for overall sample
n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) 
df_count_studies <- count_studies(df_long_for_metan )

# specify model
model_1 <- as.formula(~ four_level_var + perc_baseline_mean )

# run metareg function 
# here you can use the simulated results directly
list_model_1_meta_reg_perc <- run_metaregression(list_df_simulated, model_1)

# extract coefficients and model characteristics.
condition <- levels(list_df_simulated[[1]]$four_level_var)
aggregate_results_perc <-  aggregate_model_results(list_model_1_meta_reg_perc, condition)
aggregate_results_perc <- cbind(aggregate_results_perc, condition)

# extract SMDs from the  list
means_perc <-  lapply(list_model_1_meta_reg_perc, extract_coefficients_func)

# calculate mean SMDs and ses
df_mean_coefs_perc <- calculate_mean_coefs_ses(means_perc, condition)
df_mean_coefs_perc <- data.frame(cbind(condition,df_mean_coefs_perc))

# add the ns
df_mean_coefs_perc <- data.frame(cbind(df_mean_coefs_perc, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
